Sample size

### 2021-04-18 scripts/r/sample-size/sample-size.Rmd
edited, but doesn't run

# set weakly informative priors
# mean OR
round(mean(silber$z_score), 2)

priors <- c(
  prior(normal(0, 1), class = Intercept),
  prior(cauchy(0, 1), class = sd)
)

# run simple model
silber_sd <- brm(
  z_score ~ (1 | Team),
  data = silber,
  prior = priors,
  chain = 4,
  iter = 4000,
  cores = 4,
  backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.99999, max_treedepth = 15),
  file = "./models/sims/silber_sd"
)

>>>>

# set weakly informative priors
# mean z-score
round(mean(silber$z_score), 2)

set.seed(99)

priors <- c(
  prior(normal(2, 2), class = Intercept),
  prior(cauchy(0, 1), class = sd)
)

# run simple model
silber_sd <- brm(
  z_score ~ (1 | Team),
  data = silber,
  prior = priors,
  chain = 4,
  iter = 4000,
  cores = 4,
  #backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.99999999, max_treedepth = 15),
  file = "./models/sims/silber_sd"
)
